Homework 1

### 2019-09-05 MSimonsHW1.tex
HW 1 prob 4
Final problem for HW 1 and pdf

\item Let $a = {p_1}^{x_1} * ... * {p_k}^{x_k}$ and $b = {p_1}^{y_1} * ... * {p_k}^{y_k}$ be the prime factorizations of $a$ and $b$ respectively such that $x_i \geq 0$ and $y_i \geq 0$ for all $i \leq k$.  Let $c = {q_1}^{z_1} * ... * {q_j}^{z_j}$ be the prime factorization of $c$ given there are no $m, n$ such that $p_m = q_n$.  This holds because $(a, c) = 1$ and $(b, c) = 1$, meaning $a$ and $c$ have no common prime factors and $b$ and $c$ have no common prime factors.  Thus, $ab = {p_1}^{x_1 + y_1} * ... * {p_k}^{x_k + y_k}$.  Therefore, $ab$ and $c$ also do not have any common prime factors.  This imples that $(ab, c) = 1$.

\item TODO 4

\item TODO 5

>>>>

\item Let $a = {p_1}^{x_1} * ... * {p_k}^{x_k}$ and $b = {p_1}^{y_1} * ... * {p_k}^{y_k}$ be the prime factorizations of $a$ and $b$ respectively such that $x_i \geq 0$ and $y_i \geq 0$ for all $i \leq k$.  Let $c = {q_1}^{z_1} * ... * {q_j}^{z_j}$ be the prime factorization of $c$ given there are no $m, n$ such that $p_m = q_n$.  This holds because $(a, c) = 1$ and $(b, c) = 1$, meaning $a$ and $c$ have no common prime factors and $b$ and $c$ have no common prime factors.  Thus, $ab = {p_1}^{x_1 + y_1} * ... * {p_k}^{x_k + y_k}$.  Therefore, $ab$ and $c$ also do not have any common prime factors.  This implies that $(ab, c) = 1$.

\item Either $(a,b) = 1$ or $(a, b) \neq 1$.  First, suppose $(a, b) = 1$.  Since $a$ and $b$ do not have any common prime factors, $c$ must be a factor of $ab$ in order to be divisible by both $a$ and $b$.  Next suppose $(a, b) \neq 1$.  Let $a = {p_1}^{x_1} * ... * {p_k}^{x_k}$ and $b = {p_1}^{y_1} * ... * {p_k}^{y_k}$ be the prime factorizations of $a$ and $b$ respectively such that $x_i \geq 0$ and $y_i \geq 0$ for all $i \leq k$.  If $a$ and $b$ both divide $c$, then $m = {p_1}^{max(x_1, y_1)} * ... * {p_k}^{max(x_k, y_k)}$ is a divisor of $c$.  If $(a,b) = {p_1}^{min(x_1, y_1)} * ... * {p_k}^{min(x_k, y_k)}$, then  $m * (a,b) = ab$.  Let $c = m*x$ for some integer $x$.  Thus, $c = m*x*(a,b) = a*b*x$ is divisible by $ab$.

\item If $(a, 6) = 1$, then either $a = 6x + 1$ or $a = 6x - 1$ for some integer $x$.  Similarly, either $b = 6y + 1$ or $b = 6y - 1$.  Suppose $a = 6x + 1$.  Consequently, $a^2 = 36x^2 + 12x + 1 = 12x(3x + 1) + 1$.  Either $x$ is even or odd.  First, assume $x$ is even, so $x = 2k$ for some integer $k$.  Therefore, $a^2 = 24k(6k+1) + 1$, which leaves a remainder of 1 when divided by 24.  If $x$ is odd, then $x = 2k+1$ for some integer $k$.  As such, $a^2 = 24(6k^2 + 7k + 2) + 1$, which also leaves a remainder of 1 when divided by 24.  Next suppose, $a = 6x - 1$.  By the same logic as before, $a^2 = 24k(6k - 1) + 1$ when $x$ is even and $a^2 = 24(6k^2 + 5k +1) + 1$, both of which leave a remainder of 1 when divided by 24.  Therefore, $a^2$ always leaves a remainder of 1 when divided by 24.  By the same logic, $b^2$ also always leaves a remainder of 1 when divided by 24.  Let $a^2 = 24m + 1$ and $b^2 = 24n + 1$ for some integers $m, n < 24$.  Therefore, $a^2 - b^2 = (24m + 1) - (24n + 1) = 24(m-n)$, which is divisible by 24.
